CKY Parsing With Independence Constraints

### 2015-07-03 paper.tex
Change "parse accuracy" to "parsing accuracy"

The CKY algorithm is an \BigO{|G|n^3} dynamic programming
algorithm for finding all of the possible derivations of a sentence in
a context-free language. Its complexity depends on both the sentence
length $n$ and the size of the grammar $|G|$. Methods for improving
parse accuracy typically increase the size of the grammar 
\cite{Klein2003,Petrov2007} or even the exponent of $n$ \cite{Eisner1999}. 
More powerful “deep” grammar formalisms multiply the computational
complexity even more \cite{Bangalore1999}.

@@

For another comparison, we tested the parser using the gold independent span
boundaries. The results for section 22 are shown in Table
\ref{tbl:parse-results}. The number of binary edges visited is cut in half, and
parse accuracy is improved by almost 1 point. It is interesting to note that the
parser was unable to parse 4 sentences with the gold constraints (the grammar
only allowed a parse that violated the gold boundaries).

@@

The results are largely as expected. Sentences less than 20 words do not affect the results much. The \texttt{recall} threshold
predictably results in a large loss in classifier precision and thus parse accuracy. We note the results in
boldface: with a high precision threshold, the polynomial classifier is able to reduce the computation in the CKY loop
by 42\% while losing less than half a point in F$_{\text{1}}$ score.

>>>>

The CKY algorithm is an \BigO{|G|n^3} dynamic programming
algorithm for finding all of the possible derivations of a sentence in
a context-free language. Its complexity depends on both the sentence
length $n$ and the size of the grammar $|G|$. Methods for improving
parsing accuracy typically increase the size of the grammar 
\cite{Klein2003,Petrov2007} or even the exponent of $n$ \cite{Eisner1999}. 
More powerful “deep” grammar formalisms multiply the computational
complexity even more \cite{Bangalore1999}.

@@

For another comparison, we tested the parser using the gold independent span
boundaries. The results for section 22 are shown in Table
\ref{tbl:parse-results}. The number of binary edges visited is cut in half, and
parsing accuracy is improved by almost 1 point. It is interesting to note that the
parser was unable to parse 4 sentences with the gold constraints (the grammar
only allowed a parse that violated the gold boundaries).

@@

The results are largely as expected. Sentences less than 20 words do not affect the results much. The \texttt{recall} threshold
predictably results in a large loss in classifier precision and thus parsing accuracy. We note the results in
boldface: with a high precision threshold, the polynomial classifier is able to reduce the computation in the CKY loop
by 42\% while losing less than half a point in F$_{\text{1}}$ score.
